Peptide retention time prediction

### 2014-11-23 retention.tex
Added some text about retention time standards

\cite{irt}

>>>>

These methods involve keeping a database of previously observed
retention times for a set of peptides, and use these values as a basis
for retention time predictions. In particular, in the past years the
use of retention standards has become increasingly
widespread \cite{olegstd, irt}. Such standards typically consist of a
small number of peptides covering a wide span of hydrophobicities and
with well studied behaviors under LC-MS/MS. These peptides are often
analyzed together with the sample of interest, and by comparing their
observed and expected behaviors one can obtain valuable information
for a variety of applications.

\vspace{0.15cm}

As an example, in targeted proteomics, peptide standards can be used to
 calibrate predicted retention times and to estimate the accuracy of
 the prediction algorithms~\cite{Kiyonami01022011}. In addition,
 recent studies have reported excellent results when using peptide
 standards to adjust the time when certain transitions are scheduled
 ``on-the-fly''~\cite{seb, irt}. Retention standards are also useful
 for aligning data from multiple experiments~\cite{petritis2003}, to
 transfer retention times between different chromatography
 setups~\cite{seb}, or to keep track of the performance of LC-MS/MS
 systems~\cite{qcal}.
